### 2014-09-15 SP_simul.Rmd
Add Anderson-Darling test and power calculation

require(pander)
panderOptions('table.split.table',Inf)

@@

```{r simul_z1, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r simul_z1_512, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r simul_ls_256, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r simul_ls_512b, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_FisherSAD(8,512,F))

DqF <- rbind(DqF,compMethods_FisherSAD(64,512,F))

DqF <- rbind(DqF,compMethods_FisherSAD(256,512,F))

@@

```{r simul_neu_256, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T))

DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T))

DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T))
setwd(oldcd)
rm(nsp,side,spa)
save.image()

@@

>>>>

require(pander)
panderOptions('table.split.table',Inf)
options("scipen"=100, "digits"=4)

@@

```{r simul_z1, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r simul_z1_512, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r simul_ls_256, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r simul_ls_512b, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_FisherSAD(8,512))

DqF <- rbind(DqF,compMethods_FisherSAD(64,512))

DqF <- rbind(DqF,compMethods_FisherSAD(256,512))

@@

```{r simul_neu_256, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_NeutralSAD(8,256,T)$Dq)

DqF <- rbind(DqF,compMethods_NeutralSAD(64,256,T)$Dq)

DqF <- rbind(DqF,compMethods_NeutralSAD(256,256,T)$Dq)
setwd(oldcd)
rm(nsp,side,spa)

save.image()
```

# Test if at time 500 the model is at steady state

```{r test_neutralTime, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

simul_NeutralPlotTime(8,256,T,500,"L")
simul_NeutralPlotTime(64,256,T,500,"L")
simul_NeutralPlotTime(256,256,T,500,"L")

simul_NeutralPlotTime(8,512,T,500,"L")
simul_NeutralPlotTime(64,512,T,500,"L")
simul_NeutralPlotTime(256,512,T,500,"L")

simul_NeutralPlotTime(8,512,T,500,"U")
simul_NeutralPlotTime(64,512,T,500,"U")
simul_NeutralPlotTime(256,512,T,500,"U")

@@

Compare Neutral and Logseries using 10 simulations with KS and permutations with side =256

```{r test_SAD256, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

cc <- comp_NeutralLogseries(8,256)
compGC <-splitFields_comp(cc$comp)
DqGC   <-cc$Dq
SadGC  <-cc$SAD

cc <- comp_NeutralLogseries(64,256)
compGC <-rbind(compGC,splitFields_comp(cc$comp))
DqGC   <-rbind(DqGC  ,cc$Dq)
SadGC  <-rbind(SadGC ,cc$SAD)

cc <- comp_NeutralLogseries(256,256)
compGC <-rbind(compGC,splitFields_comp(cc$comp))
DqGC   <-rbind(DqGC  ,cc$Dq)
SadGC  <-rbind(SadGC ,cc$SAD)

setwd(oldcd)
save.image()

Compare Neutral and Logseries using 10 simulations with KS and permutations with side =512

```{r test_SAD512, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

cc <- comp_NeutralLogseries(8,512)
compGC <-rbind(compGC,splitFields_comp(cc$comp))
DqGC   <-rbind(DqGC  ,cc$Dq)
SadGC  <-rbind(SadGC ,cc$SAD)

cc <- comp_NeutralLogseries(64,512)
compGC <-rbind(compGC,splitFields_comp(cc$comp))
DqGC   <-rbind(DqGC  ,cc$Dq)
SadGC  <-rbind(SadGC ,cc$SAD)

cc <- comp_NeutralLogseries(256,512)
compGC <-rbind(compGC,splitFields_comp(cc$comp))
DqGC   <-rbind(DqGC  ,cc$Dq)
SadGC  <-rbind(SadGC ,cc$SAD)

# Simulations with side=512 not done
#
#compSP <- rbind(compSP,compKS_NeutralLogseries(8,512))
#compSP <- rbind(compSP,compKS_NeutralLogseries(64,512))
#compSP <- rbind(compSP,compKS_NeutralLogseries(256,512))
rm(cc)

setwd(oldcd)
save.image()
```

Compare Neutral and Uniform 10 simulations with KS and permutations with side 256 and 512

```{r test_SAD256U, eval=F,echo=F,message=F,warning=F}
setwd("Simul")
# Agregar una parametro meta (metacommunity) a variables para identificar
# Agregar comparacion de SAD uniforme con Neutral uniforme por KS
#
cc <- comp_NeutralUniform(8,256)
compUN <-splitFields_comp(cc$comp)
DqUN   <-cc$Dq
SadUN  <-cc$SAD

cc <- comp_NeutralUniform(64,256)
compUN <-rbind(compUN,splitFields_comp(cc$comp))
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(256,256)
compUN <-rbind(compUN,splitFields_comp(cc$comp))
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(8,512)
compUN <-rbind(compUN,splitFields_comp(cc$comp))
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(64,512)
compUN <-rbind(compUN,splitFields_comp(cc$comp))
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(256,512)
compUN <-rbind(compUN,splitFields_comp(cc$comp))
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

rm(cc)

setwd(oldcd)
# Delete duplicated fields Side2 NmSp2
compGC <- compGC[,-(6:7)]
compUN <- compUN[,-(6:7)]
# merge

compT <- rbind(compGC,compUN)
# Reorganize 
compT <- compT[,c(2,3,1,4:10)]
rm(compGC,compUN)

# merge SAD
SadT <- rbind(SadGC,SadUN)
rm(SadGC,SadUN)

# merge Dq

DqT <- rbind(DqGC,DqUN)
rm(DqGC,DqUN)

save.image()

```{r power_adtest, eval=T,echo=F,message=F,warning=F}

power <- calcPower_AD(DqT,SadT,8,256)
power <- rbind(power,calcPower_AD(DqT,SadT,64,256))
power <- rbind(power,calcPower_AD(DqT,SadT,256,256))

power <- rbind(power,calcPower_AD(DqT,SadT,8,512))
power <- rbind(power,calcPower_AD(DqT,SadT,64,512))
power <- rbind(power,calcPower_AD(DqT,SadT,256,512))

# Cada 12 cambia rep(8,12)
nsp <- c(rep(8,12),rep(64,12),rep(256,12),rep(8,12),rep(64,12),rep(256,12))
save.image()
```
